Publicity Outreach for ``Quantum interval-valued probability: Contextuality and the Born rule''

### 2018-04-14 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating....

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling...
etc. \cite{PironioAcinMassarEtAl2010,MillerShi2016} However, it is
impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the quantum theory might even be deterministic if it can be simulated
by a deterministic hidden variable model~\cite{EPR1935}. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
theorems exclude any non-local and non-contextuality deterministic
hidden variable model. However, any physical measurement can only
be done with finite precision, and Meyer~\cite{PhysRevLett.83.3751}
claimed that finite-precision measurements invalidate the spirit of
the Kochen-Specker theorem. In this investigation~\cite{THOS2018},
we employ an interval-valued framework to establish bounds on the
validity of the Kochen-Specker theorem in realistic experimental environments.
In another word, when physical measurements are precise enough, the
Kochen-Specker theorem remains valid, i.e., quantum theory should
not be simulated a non-contextuality deterministic hidden variable
model. Hence, our results provide additional trust of the randomness
of quantum theory.

>>>>

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling...
etc. \cite{PironioAcinMassarEtAl2010,MillerShi2016} However, it is
impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the quantum theory might even be deterministic if it can be simulated
by a deterministic hidden variable model~\cite{EPR1935}. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
theorems exclude any non-local and non-contextuality deterministic
hidden variable model, any physical measurement can only be done with
finite precision, and Meyer~\cite{PhysRevLett.83.3751} claimed that
finite-precision measurements invalidate the spirit of the Kochen-Specker
theorem, i.e., quantum theory with finite-precision measurements might
be non-contextual. In our investigation~\cite{THOS2018}, we employ
an interval-valued framework to establish bounds on the validity of
the Kochen-Specker theorem in realistic experimental environments.
In another word, when physical measurements are precise enough, the
Kochen-Specker theorem remains valid, i.e., quantum theory remains
contextual. Hence, our results provide additional trust of the randomness
of quantum theory.
